Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-17 prob.tex
prob.tex \section{Proofs} Global replace rotation by only allow π/2...

\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
is a approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
then the \emph{symmetrization} of $f$ with respect to $\ket{0}$
is the function~$g_{f,\ket{0}}:S^{2}\rightarrow\mathbb{R}$ defined
by
\[
g_{f,\ket{0}}\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\ket{0}\times\ket{\psi}\right)\textrm{ .}
\]
Notice that $\ket{0}\times\ket{\psi}$ is the vector~$\ket{\psi}$
clockwise-rotated by $\frac{\pi}{2}$ about $\ket{0}$.\qed\end{definition}

@@

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

Then, \footnote{\yutsung{Verify the details. Especially the left-handed or right-handed
of the coordinate system, and the rotation matrix... >''<}} 
\begin{eqnarray*}
\ket{0}\times\left(x,y,z\right) & = & \left(x,-z,y\right)\\
\ket{2}\times\left(x,y,z\right) & = & \left(-y,x,z\right)
\end{eqnarray*}
Note that 
\begin{eqnarray*}
Q\left(\ket{\psi}\right)+Q\left(\ket{0}\times\ket{\psi}\right) & = & 2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\\
Q\left(\ket{\psi}\right)+Q\left(\ket{2}\times\ket{\psi}\right) & = & 2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)
\end{eqnarray*}
which is the same as the quadratic form defined in corollary~\ref{thm:analogCorollary22RichmanBridges1999}.
Therefore, by corollary~\ref{thm:analogCorollary22RichmanBridges1999},
we should have 
\begin{eqnarray*}
\left|f'\left(\ket{\psi}\right)+f'\left(\ket{0}\times\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
\left|f'\left(\ket{\psi}\right)+f'\left(\ket{2}\times\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
\end{eqnarray*}
Follow the same procedure in the proof in \cite{RichmanBridges1999}.
We have
\[
\left|f'\left(\ket{\psi}\right)\right|=\left|f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
\]
on the six great circles~$x=\pm y$, $y=\pm z$, and $z=\pm x$ on
$S^{2}$. In particular, 
\[
\left|f\left(\ket{\psi}\right)-M\left(x^{2}-z^{2}\right)-Wz^{2}\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
\]
 on the great circle~$y=z$.

@@

\begin{claim}~
\begin{itemize}
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\left(\ket{0}\times\ket{\bar{0}}\right)\times\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
\begin{proof}
For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\sum_{i=1}^{2}\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\left|\ip{i}{\psi}\right|\right)\right|
\end{eqnarray*}
In order to estimate the last equation, we need to verify the conditions
listed in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.

@@

This proof will be separated into two parts. The first part will estimate
the error between the approximation frame function and the quadratic
form on every complex two-space. The second part will then verify
the quadratic forms in the first part could be connected and get a
quadratic form on the whole space.

\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
\begin{itemize}
\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
\[
\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
\]
\item $\ket{\psi_{2}}=\ket{\psi_{0}}\times\ket{\psi_{1}}\in\mathbb{C}S^{2}$.
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
\end{proof}
}

>>>>

\begin{definition}Given a vector~$\ket{\psi}\in\mathbb{C}^{3}$,
$\sigma_{\ket{\psi}}$ is the clockwise rotation by $\frac{\pi}{2}$
about $\ket{\psi}$. More explicitly, for any vector~$\ket{\phi}\in\mathbb{C}S^{2}$,
$\sigma_{\ket{\psi}}\ket{\phi}=\frac{\ket{\psi}\times\ket{\phi}}{\left\Vert \ket{\psi}\times\ket{\phi}\right\Vert }$.\qed\end{definition}

\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
is a approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
then the \emph{symmetrization} of $f$ with respect to $\ket{0}$
is the function~$g_{f,\ket{0}}:S^{2}\rightarrow\mathbb{R}$ defined
by
\[
g_{f,\ket{0}}\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0}}\ket{\psi}\right)\textrm{ .}
\]
\qed\end{definition}

@@

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

Then, \footnote{\yutsung{Verify the details. Especially the left-handed or right-handed
of the coordinate system, and the rotation matrix... >''<}} 
\begin{eqnarray*}
\sigma_{\ket{0}}\left(x,y,z\right) & = & \left(x,-z,y\right)\\
\sigma_{\ket{2}}\left(x,y,z\right) & = & \left(-y,x,z\right)
\end{eqnarray*}
Note that 
\begin{eqnarray*}
Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0}}\ket{\psi}\right) & = & 2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\\
Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{2}}\ket{\psi}\right) & = & 2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)
\end{eqnarray*}
which is the same as the quadratic form defined in corollary~\ref{thm:analogCorollary22RichmanBridges1999}.
Therefore, by corollary~\ref{thm:analogCorollary22RichmanBridges1999},
we should have 
\begin{eqnarray*}
\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
\end{eqnarray*}
Follow the same procedure in the proof in \cite{RichmanBridges1999}.
We have
\[
\left|f'\left(\ket{\psi}\right)\right|=\left|f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
\]
on the six great circles~$x=\pm y$, $y=\pm z$, and $z=\pm x$ on
$S^{2}$. In particular, 
\[
\left|f\left(\ket{\psi}\right)-M\left(x^{2}-z^{2}\right)-Wz^{2}\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
\]
 on the great circle~$y=z$.

@@

\begin{claim}~
\begin{itemize}
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
\begin{proof}
For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\sum_{i=1}^{2}\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\left|\ip{i}{\psi}\right|\right)\right|
\end{eqnarray*}
In order to estimate the last equation, we need to verify the conditions
listed in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.

@@

\yutsung{
\begin{proof}
~
\begin{proof}
This proof will be separated into two parts. The first part will estimate
the error between the approximation frame function and the quadratic
form on every complex two-space. The second part will then verify
the quadratic forms in the first part could be connected and get a
quadratic form on the whole space.
\end{proof}
\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
\begin{itemize}
\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
\[
\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
\]
\item $\ket{\psi_{2}}=\ket{\psi_{0}}\times\ket{\psi_{1}}\in\mathbb{C}S^{2}$.
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
\end{proof}
}
